---
title: "Newspapers in Times of Low Advertising Revenues ^[Code and data are available at:https://github.com/Faustine123/Newspapers-in-Times-of-Low-Advertising-Revenues]"
author: "Faustine Fan"
date: "5 April 2023"
date-format: long
abstract: "Newspaper(Will add after I finished this paper:)"
format: pdf
documentclass: article
geometry: margin = 1in 
bibliography: references.bib
---
## 1. Introduction

As the world undergoes digital transformation, the newspaper industry faces many challenges that affect their circulation, content quality and pricing strategies.As noted by Alotaibi and Sultan [@2015alotaibi], the emergence of mobile devices and the increase in online news consumption have led newspapers to create digital versions of their publications to attract new readers and advertisers. One important point is that the digitization of people's lives has led to a decline in newspaper subscriptions and advertisers have changed the placement of some of their ads in response to changing market demand. Since advertising revenue is an important source of revenue for newspapers, a decrease in advertising may lead to a decrease in the number of issues printed and distributed as well as the quality of content produced. This in turn could affect the number of journalists employed, their salaries, and the quality of the important stories they cover.

It is an interesting phenomenon that as newspaper content, pricing strategies change, the education and property levels of subscribers fluctuate. In addition, national and local newspapers may have different pricing strategies depending on their target audience and advertising revenue. The relationship between newspapers and their advertising suppliers and subscribers may also be affected by reduced advertising revenues, leading to potential conflicts of interest.

In addition, newspapers may resort to price discrimination strategies, such as offering discounts to long-term subscribers, to maintain their customer base. the rise of television advertising in the 20th century and the transition from black-and-white to color television may also affect the demand for newspapers and their ability to attract advertisers. When the Internet wave hit, newspapers faced another wave of impact.

Given these challenges, it is important to examine the strategies newspapers have adopted in an era of low advertising and how they are adapting to changing market conditions to ensure their survival and relevance in today's media environment. The purpose of this research paper is to examine the impact of low advertising on the newspaper industry, the pricing strategies employed by newspapers, and the relationship between newspapers, advertisers, and subscribers.

## 2. Data

### 2.1 Source

### 2.2 Methodology

This analysis will be performed in R [@R], using the dplyr [@dplyr], readxl [@readxl], tidyr [@tidyr], data.table [@table], lubridate [@lube], haven [@haven], and tidyverse [@tidy] packages. All figures in the report are generated using ggplot2 [@ggplot].

The collection method of our sources varies. For @fig-2, 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.width=6.5, fig.height=2.8) 

# loading in relevant libraries
library(tidyverse)
library(dplyr, warn.conflicts = FALSE)
library(tidyr)
library(readxl)
library(data.table)
library(lubridate)
library(haven)
library(readxl)
library(ggplot2)
library(scales)
### Input data ###
figure1_rawdata<-read_dta(here::here("Input/Data/Angelucci_Cage_AEJMicro_dataset.dta"))
figure2_rawdata<-read_dta(here::here("Input/Data/Angelucci_Cage_AEJMicro_Descriptive_evidence_advertisement.dta"))
figure3_rawdata<-read_dta(here::here("Input/Data/Angelucci_Cage_AEJMicro_Descriptive_evidence_advertising_industry.dta"))
figure4_rawdata<-read_dta(here::here("Input/Data/Angelucci_Cage_AEJMicro_Descriptive_evidence_television_quality.dta"))
figure5_rawdata<-read_dta(here::here("Input/Data/Angelucci_Cage_AEJMicro_Descriptive_evidence_US.dta"))

```

### 2.2 Features

## 3. Results


The code of the graph have some issue now :) 
```{r}
#| label: fig-1revenuesjournalists
#| fig-cap: The Counterrelationship between Newspaper Revenue and the Number of Daily Journalists
#| message: false
#| warning: false
#| echo: false

# create a line graph
figure1_rawdata |>
  ggplot( mapping = aes(x = year, y = ra_cst + nb_journ)) +
  geom_line(aes(y = ra_cst), color = "blue") +
  scale_y_continuous(
    name = "Million US$",
    labels = c("10,000", "20,000", "30,000", "40,000", "50,000"),
    breaks = c(10000, 20000, 30000, 40000, 50000),
    sec.axis = sec_axis(trans = ~., name = "Number of daily newspaper journalists",
                        labels = c("30,000", "35,000", "40,000", "45,000", "50,000", "55,000", "60,000"),
                        breaks = c(30000, 35000, 40000, 45000, 50000, 55000, 60000),
                        )) +
  geom_line(aes(y = nb_journ/5,000), color = "red") +
  labs(y = "Million US$", title = "Newspapers' advertising revenues vs Number of daily newspaper journalists") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8),
        axis.text.y = element_text(angle = 0, hjust = 1, vjust = 1, size = 8))
```


```{r}
#| message: false
#| warning: false
#| echo: false
#| label: fig-2
#| fig-cap: ""

```

```{r}
#| message: false
#| warning: false
#| echo: false
#| fig-cap: ""
#| label: fig-5

### Draw graph ###
```

## 4. Discussion

### 4.1 Findings

### 4.2

### 4.3 Ethical Implications

### 4.4 Potential Bias

### 4.5 Limitations of the Paper

### 4.6 Possible Next Steps

{{< pagebreak >}} \## References
